TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-07-28 paper/draft.tex
add discussion paragraph

\begin{figure*}[]
\begin{center}
	\includegraphics[width=.32\linewidth]{figures/met_comp1.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp2.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp3.png} 
	\includegraphics[width=.32\linewidth]{figures/met_comp4.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp5.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp6.png} 
	\includegraphics[width=.32\linewidth]{figures/met_comp7.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp8.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp9.png} 
	\caption{A comparison of ASPCAP and Cannon metallicities for 8,335 test sample sources separated into temperature bins of 100K. We see the scatter and metal-poor bias of ASPCAP metallicities clearly increases at decreasing temperatures.}
\end{center}
\end{figure*}

@@

>>>>

\begin{figure*}[]
\begin{center}
	\includegraphics[width=.32\linewidth]{figures/met_comp1.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp2.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp3.png} 
	\includegraphics[width=.32\linewidth]{figures/met_comp4.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp5.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp6.png} 
	\includegraphics[width=.32\linewidth]{figures/met_comp7.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp8.png}
	\includegraphics[width=.32\linewidth]{figures/met_comp9.png} 
	\caption{A comparison of ASPCAP and Cannon metallicities for 8,335 test sample sources separated into temperature bins of 100K. We see the scatter and metal-poor bias of ASPCAP metallicities clearly increases at decreasing temperatures.} 
	\label{fig:met_comp}
\end{center}
\end{figure*}

@@

While a detailed analysis of atmospheric model limitations is beyond the scope of this paper, 
our results provide an avenue to compare the FGK star metallicity scale 
to the less well-understood M dwarf metallicity scale.
These results find that atmospheric metallicities are systematically metal-poor biased
compared to \cannon-based metallicities trained on sources with metallicities callibrated
to those of FGK companions. 
At the high temperature end ($\teff > 3600$\,K), the ASPCAP metallicity bias is $\sim-0.15\,$dex with a
scatter of $\sim0.06\,$dex relative to \cannon\ metallicities, and increases to a bias of $\>-0.26\,$dex 
and scatter of $\>0.1\,$dex at the lower temperature end ($\teff < 3300$\,K) (Figure \ref{fig:met_comp}).
This metal-poor bias, while not explored to a great extent in this work, we suspect is due 
to the line lists of the models: 
an effect in which the optimizer of the pipeline may be lowering the metallicity of the fit 
to better reproduce the spectrum to compensate for the missing lines or opacities.
Further analysis would need to be done to determine if the metallicity bias
is found in other model grids (besides the ATLAS/MARCS models used by the ASPCAP pipeline), 
and if the effect is present at other wavelengths.
